TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-03-26 article.tex
TTT: nueva imagen atp

\en{We attach the \proglang{Julia} and \proglang{R} codes that solve the example presented in the section \ref{sec:skill_evolution} about estimation the skill evolution of a new player.}
\es{Adjuntamos los códigos de \proglang{Julia} y \proglang{R} que resuelven el ejemplo presentado en la sección \ref{sec:skill_evolution} sobre la evolución de habilidad de un jugador nuevo.}
%
\begin{lstlisting}[backgroundcolor=\color{julia},caption={\en{\prolang{Julia} code}\es{}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
using Random; Random.seed!(999); N = 1000
function skill(experience, middle, maximum, slope)
    return maximum/(1+exp(slope*(-experience+middle))) 
end
target = skill.(1:N, 500, 2, 0.0075)
opponents = Random.randn.(1000)*0.5 .+ target

@@

h = ttt.History(composition, results, times, priors, gamma=0.015)
ttt.convergence(h)
mu = [tp[2].mu for tp in ttt.learning_curves(h)["a"]]
\end{lstlisting}
%
\begin{lstlisting}[backgroundcolor=\color{r},caption={\en{\prolang{R} code}\es{}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
N = 1000
skill <- function(experience, middle, maximum, slope){
    return(maximum/(1+exp(slope*(-experience+middle)))) }
target = skill(seq(N), 500, 2, 0.0075)
opponents = rnorm(N,target,0.5)

>>>>

\en{We attach the \proglang{Julia} and \proglang{R} codes that solve the example presented in the section \ref{sec:skill_evolution} about estimation the skill evolution of a new player.}
\es{Adjuntamos los códigos de \proglang{Julia} y \proglang{R} que resuelven el ejemplo presentado en la sección \ref{sec:skill_evolution} sobre la evolución de habilidad de un jugador nuevo.}
%
\begin{lstlisting}[backgroundcolor=\color{julia},caption={\en{\proglang{Julia} code}\es{Código \proglang{Julia}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
using Random; Random.seed!(999); N = 1000
function skill(experience, middle, maximum, slope)
    return maximum/(1+exp(slope*(-experience+middle))) 
end
target = skill.(1:N, 500, 2, 0.0075)
opponents = Random.randn.(1000)*0.5 .+ target

@@

h = ttt.History(composition, results, times, priors, gamma=0.015)
ttt.convergence(h)
mu = [tp[2].mu for tp in ttt.learning_curves(h)["a"]]
\end{lstlisting}
%
\begin{lstlisting}[backgroundcolor=\color{r},caption={\en{\proglang{R} code}\es{Código \proglang{R}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
N = 1000
skill <- function(experience, middle, maximum, slope){
    return(maximum/(1+exp(slope*(-experience+middle)))) }
target = skill(seq(N), 500, 2, 0.0075)
opponents = rnorm(N,target,0.5)
